The Rockerverse: Packages and Applications for Containerisation with R

### 2020-06-09 README.Rmd

Article about everything related to containers and R, originally based on the blog post http://bit.ly/docker-r and now **available as a preprint on arXiv.org: https://arxiv.org/abs/2001.10641**.

_Want to contribute?_ See https://github.com/nuest/rockerverse-paper/issues/3.

@@

# For submission to arXiv:
# 1. Copy the following files into a new folder:
# - figures/*
# - rockerverse.tex
# - RJournal.sty
# - RJreferences.bib
# - RJwrapper.tex
# 2. Run pdfLaTeX directly on RJwrapper.tex (works with RStudio)
# 3. Zip the following files and submit to arXiv:
# - /figures
# - rockerverse.tex
# - RJournal.sty
# - RJwrapper.bbl
# - RJwrapper.tex
```

@@

>>>>

Article about everything related to containers and R, originally based on [this blog post](http://bit.ly/docker-r) and now **available as a preprint on arXiv.org: https://arxiv.org/abs/2001.10641**.

@@

# For submission to arXiv:
# 1. Copy the following files into a new folder:
# - figures/*
# - rockerverse.tex
# - RJournal.sty
# - rockerverse.bib
# - RJwrapper.tex
# 2. Run pdfLaTeX directly on RJwrapper.tex (works with RStudio)
# 3. Zip the following files and submit to arXiv:
# - /figures
# - rockerverse.tex
# - RJournal.sty
# - RJwrapper.bbl
# - RJwrapper.tex
```

@@

```{r submission_zipfile, eval=FALSE, include=FALSE}
# Please upload a zip file of the directory containing a motivating letter (in PDF format) if required, the sources of your article; the *.tex, *.bib and *.R files should have the same file name before the extension, which should be your last or family name in lower-case letters, or the last or family names of the authors joined using hyphens. Your title should not include dashes or hyphens. Make sure to also include RJwrapper.tex and RJwrapper.pdf. 
zip::zip("rockerverse.zip", c("rockerverse.tex",
                              "rockerverse.bib",
                              "rockerverse.R",
                              "figures/orcid.pdf",
                              "figures/Rlogo.pdf",
                              "RJwrapper.tex",
                              "RJwrapper.pdf"))
```
